\subsection{Drucker-Prager Plasticty Model With Ductile Damage}

{*}drucker prager plsticity model used for modelling frictional materailas
like granual soils and rock.

{*} these materials exhibit pressure dependant yeilding (as confining
presure increases, so does the strength of the rock) which is accounted
for in this model

{*}used for materials in which the compressive yeild strength is much
greater than the tensile yeild strength (again, rocks and soils)

{*}D-P can be used in conjunction with the models of progressive damage
and failure.

{*}one drawback with this material model is that it is intended to
simulate material response under essentially monotonic loading. 

The linear Drucker-Prager yeild function, which defines the pressure
dependant behaviour of the material can be written as follows:

\begin{equation}
F=t-p\tan\left(\beta\right)-d\label{eqn:druc1}
\end{equation}


In this paper, the hyperbolic Drucker-Prager yeild function is chosen
to represent the material behaviour:

\begin{equation}
F\left(p,q\right)=\sqrt{l_{0}^{2}+q^{2}}-p\tan\left(\beta\right)-d\label{eqn:druc2}
\end{equation}


where:

\begin{equation}
l_{o}=d'_{0}-p_{0}^{t}\tan\left(\beta\right)\label{eqn:druc2-1}
\end{equation}


The hyperbolic model uses a von Mises section in the deviatoric stress
plane and a hyperbolic flow potential in the meridontal plane. This
means non-associated flow. Hyperbolic model assumes a linear dependance
between deviatoric stress and hydrostatic stress at high confining
stresses, but allows for a non-linear relationship at low confining
stress. If tensile stresses are significant, the hyperbolic model
should be used.

From above, $q$ and $p$ represent two stress invariants, the mises
equivalent stress and the equivalent pressure stress(hydrostatic stress):

\begin{equation}
p=-\frac{1}{3}tr\left(\boldsymbol{\sigma}\right)\label{eqn:druc3}
\end{equation}


\begin{equation}
q=\sqrt{\frac{3}{2}}\left(\mathbf{S}\vcentcolon\mathbf{S}\right)\label{eqn:druc4}
\end{equation}


where $S$ is the stress deviator:

\begin{equation}
\mathbf{S}=\boldsymbol{\sigma}+p\mathbf{I}\label{eqn:druc4-1}
\end{equation}


and I is the second order identity tensor. This hyperbolic yeild critereon
is a combination of Rankine's maximum tensile stress condition at
low confining stress anf the linear Drucker-Prager condition at high
confining stress.

Flow Rule, same as concrete damage. should bring to main d-p material
description:

\begin{equation}
G=\sqrt{\left[\epsilon\bar{\sigma}_{0}\tan\left(\psi\right)\right]^{2}+q^{2}}-p\tan\left(\psi\right)\label{eqn:druc5}
\end{equation}


default value of eccentricity: maybe

\begin{equation}
\epsilon=\label{eqn:druc5-1}
\end{equation}


Hardening Rule -> not sure best way to write this

\begin{equation}
h=h\left(d',\bar{\sigma}\right)\label{eqn:druc6}
\end{equation}


where:

\begin{equation}
d'=\sqrt{l_{0}^{2}+\sigma_{c}^{2}}-\frac{\sigma_{c}}{3}\tan\left(\beta\right)\label{eqn:druc6-1}
\end{equation}


isotropic hardening is assumed, treating friction angle constant wrt
stress

{*}Damage initiation

- assume ductile damage. at large confining pressures at large scale,
the behaviour of rock is more ductile than brittle.

- onset of damage due to `` nucleation, growth, and coalescnce of
voids''. Model assumes PEEQ when damage is initiated is a function
of triaxiality, eta.

assume the form of the Johnson-Cook Model:

\begin{equation}
\bar{\epsilon}_{f}^{pl}\left(\eta,\dot{\bar{\epsilon}}^{pl},\hat{T}\right)=\left[D_{1}+D_{2}e^{D_{3}\eta}\right]\left[1+D_{4}\ln\left(\frac{\dot{\bar{\epsilon}}^{pl}}{\dot{\bar{\epsilon}}}\right)\right]\left[1+D_{5}\hat{T}\right]\label{eqn:druc7}
\end{equation}


assuming isothermal conditions and neglecting strain rate effects
because of reasons:

\begin{equation}
\bar{\epsilon}_{f}^{pl}\left(\eta\right)=\left[D_{1}+D_{2}e^{D_{3}\eta}\right]\label{eqn:druc8}
\end{equation}


{*}Damage evolution:

- assumes damage is a progressive degredation of the material stiffness

- assume isotropic damage

- uses mesh independant measure of plastic dispalcement to drive evolution
of damage

- damage manifests itself in two forms: softenin of the yeild stress
and degredation of the elastisity.

Damage evolution equation based on effective plastic displacement:

\begin{equation}
\dot{\bar{u}}^{pl}=L\dot{\bar{\epsilon}}^{pl}\label{eqn:druc9}
\end{equation}


asuming a linear form, the plastic displacement at at complete damage
