\subsection{Assessment of the REV Size}

Homogenizing DEM simulations requires the existence and determination of the REV for that medium. Generally, the REV of a given domain can be described as the smallest subdomain that is statistically representative of the entire domain \citep{Kanit_2003, Gitman_2007}. This qualitative definition is insufficient to rigorously define an REV as it is subjective with respect to what “statistically representative” means. Hence, the assessment of the REV can be a contentious issue, fraught with ambiguity.

One can conceptualize an REV to be “statistically representative” in two primarily different ways \citep{Drugan_1996}. The classically cited means for characterizing an REV suggests that the micro-scale heterogeneities (e.g. fractures, voids, grains, etc.) should be statistically representative within the REV such that the REV should contain a sufficiently large sample of these heterogeneities. This characterization of the REV is potentially problematic when attempting to quantify the REV as the descriptions of these heterogeneities tend to be nominally qualitative, and at best, quasi-quantitative.

The alternative means of conceptualizing “statistically representative”, and arguably a more pragmatic way, proposes that the constitutive response of the REV should be statistically representative of the domain. In other words, as one increases the size of a sample domain, the point at which the constitutive response within the domain becomes sensibly constant can be referred to as the REV. Thus, the subdomain constitutive response is quantifiable through resultant model properties and parameters. This REV interpretation has been widely used because of its quantifiability \citep{Kanit_2003, Gitman_2005, Gusev_1997, M_ller_2010}, and is adopted for this work.