\subsection{Stress Homogenization}
The homogenized Cauchy stress, $\langle \boldsymbol{\sigma} \rangle$, is derived from the definition of the spatial average of the stress, $\boldsymbol{\sigma}$, over the homogenization domain $\Omega^h$, with an area $A^h$:
\begin{equation}
\label{eqn:stress1}
\langle \boldsymbol{\sigma} \rangle = \frac{1}{A^h} \int_{\Omega^h} \boldsymbol{\sigma} {dA}
\end{equation}

As previously mentioned, there exists a nesseccary distinction between the block subdomain and the void subdomain when dealing with stress. Here, the integration over the homogenization domain can be decomposed into two seperate integrations over the block subdomain and the void subdomain:
\begin{equation}
\label{eqn:stress2}
\langle \boldsymbol{\sigma} \rangle = 
\frac{1}{A^h} \bigg \lbrack {\int_{\Omega^{b}} \boldsymbol{\sigma} {dA} + 
\int_{\Omega^{v}} \boldsymbol{\sigma} {dA}} \bigg \rbrack
\end{equation}

This distinction is made due to the fact that in a purely mechanical model, there isn't any pressure or stress being retained in the void space, resulting in a negligable contribution to the overall stress state. This allows for the void subdomain integration term to be dropped from the formulation:
\begin{equation}
\label{eqn:stress2a}
\langle \boldsymbol{\sigma} \rangle = 
\frac{1}{A^h} \int_{\Omega^{b}} \boldsymbol{\sigma} {dA}
\end{equation}

Since the block subdomain is inherently discretized, the integration of the stress over the block subdomain can be written as a summation of the average stress in each block, $\boldsymbol{\sigma}^b_i$, of area $A^b_i$over $N^b$ number of blocks in the block subdomain:
\begin{equation}
\label{eqn:stress3}
\langle \boldsymbol{\sigma} \rangle = 
\frac{1}{A^h} \sum_{i=1}^{N^{b}} \boldsymbol{\sigma}_{i}^b A^{b}_{i} 
\end{equation}

*In the case where the blocks are considered deformable, the average stress in a given block can be assessed by taking a spatially weighted average of the zone stresses. *explain how stresses are calculated
\begin{equation}
\label{eqn:stress3a}
\boldsymbol{\sigma}_{i}^b = 
\frac{1}{A^b_i} \sum_{j=1}^{N^{z}_i} \boldsymbol{\sigma}^z_{ij} A^{z}_{ij} 
\end{equation}

Combining equations \ref{eqn:stress3} and \ref{eqn:stress3a} yeild the final form for assessing the homogenized Cauchy stress tensor for deformable DEM blocks:
\begin{equation}
\label{eqn:stress4}
\langle \boldsymbol{\sigma} \rangle = 
\frac{1}{A^h} \sum_{i=1}^{N^{b}} \sum_{j=1}^{N^{z}_i} \boldsymbol{\sigma}^z_{ij} A^{z}_{ij} 
\end{equation}


In this investigation, the DEM simulations considered deformable blocks. Each one of these blocks is discretized into zones, in which the stresses are calculated at each time step. As such, the homogenization procedure can be simplified to a weighted average of the stresses in the zones. The integral (2) can be rewritten as a summation: 


	
where the homogenization domain contains $N_b$ number of blocks, each containing $N_z^i$ number of zones. $\boldsymbol{\sigma}_z^ij$ and $A_z^ij$ are the stress tensor and area of the jth zone of the ith block in the homogenization domain, respectively.